\documentclass[12pt]{article}
% \usepackage{fullpage}
\usepackage{graphics,graphicx,subfig}
\usepackage{amsmath,multicol,lscape,framed,amssymb}
\usepackage{graphicx,epic,subfig,graphicx,tikz,pifont}
%\usepackage{multirow,epic}
% \usepackage{algorithmic,algorithm}
\usepackage{hyperref,hypcap}
\usepackage{natbib}%
\usepackage{longtable}
\usepackage{textcomp}%to use \textquotesingle
% \captionsetup{type=figure}
\hypersetup{
colorlinks,%
citecolor=blue,%
filecolor=black,%
linkcolor=blue,%
urlcolor=blue,
}
\usepackage{setspace}
\bibliographystyle{chicago}

\bibstyle{plain}
\newcommand{\HRule}{\noindent\rule{\linewidth}{1.5pt}}
\newtheorem{alg}{Algorithm}
\newcommand{\cm}[1]{\begin{center}{\tt #1}\end{center}}
\newcommand{\hs}{{\tt hybrid-coal}}
\newcommand{\PP}{{\mathbb P}}


\begin{document}

\title{Hybrid-coal manual}
\author{Sha (Joe) Zhu}
\maketitle

\input{coal_manual.tex}

\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{Brumfield and Carling}{Brumfield and
  Carling}{2010}]{Brumfield2010}
Brumfield, R.~T. and M.~D. Carling (2010).
\newblock The influence of hybrid zones on species tree inference in manakins.
\newblock In L.~L. Knowles and L.~S. Kubatko (Eds.), {\em Estimating Species
  Trees, Practical and Theoretical Aspects}, pp.\  115--127. Hoboken, NJ:
  Wiley-Blackwell.

\bibitem[\protect\citeauthoryear{Buckley, Cordeiro, Marshall, and
  Simon}{Buckley et~al.}{2006}]{Buckley2006}
Buckley, T.~R., M.~Cordeiro, D.~C. Marshall, and C.~Simon (2006).
\newblock Differentiating between hypotheses of lineage sorting and
  introgression in {New Zealand} alpine cicadas (\emph{{M}aoricicada
  {D}ugdale}).
\newblock {\em Systematic Biology\/}~{\em 55\/}(3), 411--425.

\bibitem[\protect\citeauthoryear{Cardona, Rossell, and Valiente}{Cardona
  et~al.}{2008}]{Cardona12008}
Cardona, G., F.~Rossell, and G.~Valiente (2008).
\newblock Extended {N}ewick: it is time for a standard representation of
  phylogenetic networks.
\newblock {\em BMC Bioinformatics\/}~{\em 9\/}(532-540).

\bibitem[\protect\citeauthoryear{Degnan and Salter}{Degnan and
  Salter}{2005}]{Degnan2005}
Degnan, J.~H. and L.~A. Salter (2005).
\newblock Gene tree distributions under the coalescent process.
\newblock {\em Evolution\/}~{\em 59}, 24--37.

\bibitem[\protect\citeauthoryear{Holland, Benthin, Lockhart, Moulton, and
  Huber}{Holland et~al.}{2008}]{Holland2008}
Holland, B.~R., S.~Benthin, P.~J. Lockhart, V.~Moulton, and K.~T. Huber (2008).
\newblock Using supernetworks to distinguish hybridization from
  lineage-sorting.
\newblock {\em BMC Evolutionary Biology\/}~{\em 8}, 202--213.

\bibitem[\protect\citeauthoryear{Huson, Rupp, and Scornavacca}{Huson
  et~al.}{2010}]{Huson2010}
Huson, D., R.~Rupp, and C.~Scornavacca (2010).
\newblock {\em Phylogenetic Networks: Concepts, Algorithms and Applications}.
\newblock Cambridge, UK: Cambridge University Press.

\bibitem[\protect\citeauthoryear{Meng and Kubatko}{Meng and
  Kubatko}{2009}]{Meng2009}
Meng, C. and L.~S. Kubatko (2009).
\newblock Detecting hybrid speciation in the presence of incomplete lineage
  sorting using gene tree incongruence: a model.
\newblock {\em Theoretical Population Biology\/}~{\em 75}, 35--45.


\end{thebibliography}

\end{document}

